Estimating individual subjective values of emotion regulation strategies

### 2022-02-21 06_Paper/ER-ED/Manuscript_ERED_Stage1.tex
knitted document

Every day we are confronted with stressful or emotionally demanding situations.
The ability to modify emotional experiences, expressions, and physiological reactions\textsuperscript{1} to regulate emotions is an important cognitive skill.
It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning.\textsuperscript{2}
Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification,\textsuperscript{1} and, following the taxonomy of Powers and LaBar,\textsuperscript{3} individuals can implement ER strategies by means of different tactics.
So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process.\textsuperscript{1}
In contrast, response modification takes place late in the process and is therefore conceptualized as a response-focused strategy.\textsuperscript{1}
This postulated temporal sequence of ER strategies influences their effectiveness.
It is meta-analytically proven that all mentioned strategies reduce subjective emotional arousal.\textsuperscript{4}
Distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed small to medium effect sizes on measures of emotional experience (distraction: \emph{d\textsubscript{+}} = 0.27; suppression: \emph{d\textsubscript{+}} = 0.27).
Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of \emph{d\textsubscript{+}} = 0.45.\textsuperscript{4}
Moreover it is known that ER strategies reduce physiological arousal, measured via EMG in the region of the \emph{corrugator supercilii}.\textsuperscript{5}
So these tactics from three different strategies proved to be effective in the short term.
However, in order to be able to make a statement on their general benefit, longer-term consequences must also be considered.
Especially strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
Long-term consequences of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed.\textsuperscript{6}
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of \emph{adaptive} and \emph{maladaptive} strategies.
For example, it could be shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms.\textsuperscript{7}
Also, a number of ER strategies is linked to psychological disorders (for meta-analytic review, see).\textsuperscript{8}

The postulation of \emph{adaptive} and \emph{maladaptive} strategies was put in a new perspective with the concept of ER flexibility.
Similar to other psychological domains, e.g., attention and goal pursuit, \emph{maladaptive} now refers to inflexible strategy use or use of strategies that are hindering the achievement of goals.\textsuperscript{9}
Adaptive flexible ER requires having a large repertoire of ER strategies.\textsuperscript{9}
For example, greater ER variability is related to reduced negative affect and therefore beneficial in daily life.\textsuperscript{10}
Strategies have to be chosen from the repertoire that are useful for goal achieving.
Evidence from other contexts (e.g., intertemporal choice,)\textsuperscript{11} shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs.
For example, it was shown that the intensity of a stimulus or situation plays a role in the choice.\textsuperscript{12}
Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction.\textsuperscript{12,13}
Further influencing factors are for example extrinsic motivation (e.g.~monetary incentives), motivational determinants (i.e.~hedonic regulatory goals), and effort.\textsuperscript{13,14}
Especially for effort, in our previous work we could show that the choice for an ER strategy is mainly influenced by effort.\textsuperscript{14}
In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards they could choose, which strategy they want to use again.
Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one - in this case: Suppression.
Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
What has been missing in research on ER choice so far is information regarding the strategy \emph{not} chosen.
People choose a strategy that they prefer, for different, relatively well-known reasons.
However, nothing is revealed about the strategy that is not chosen.

The postulation of \emph{adaptive} and \emph{maladaptive} strategies was put into a new perspective with the concept of ER flexibility.
Similar to other psychological domains such as attention and goal pursuit, \emph{maladaptive} now refers to inflexible strategy use or use of strategies that are hindering the achievement of goals.\textsuperscript{9}
In contrast, \emph{adaptive} ER requires having a large repertoire of ER strategies to choose from\textsuperscript{9} and choosing the strategy that is useful for goal achieving in a particular situation.
This greater ER variability has been shown to be related to reduced negative affect.\textsuperscript{10}
The process of choosing an ER strategy from one's own repertoire likely shares similarities with other contexts such as intertemporal choice, in which individuals assign subjective values to every choice option.\textsuperscript{11}
Additionally, there are ER-specific influences on choice behaviour such as the intensity of the stimulus or situation, which leads to a choice of rather disengaging strategies like distraction, extrinsic motivation (e.g.~monetary incentives), motivational determinants (i.e.~hedonic regulatory goals), and effort.\textsuperscript{13,14}
Effort in particular appeared to be the main factor in ER choice behaviour in our previous work.\textsuperscript{14}
In that study, participants used the strategies distancing and suppression while inspecting emotional pictures, and could choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one for them - in this case: Suppression.
Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
Research on ER choice has shown that individuals choose a strategy that they prefer for different, relatively well-known reasons.
However, nothing has been investigated regarding the strategy that is \emph{not} chosen.

We assume that people choose the strategy that has the highest value for them at that moment.
The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement.\textsuperscript{9}
One certainly central goal is the regulation of negative affect.
A second, intrinsic and rather less obvious goal is the avoidance of effort.\textsuperscript{15}
When given the choice, most individuals prefer tasks that are less effortful.\textsuperscript{16}
We assume that both aspects are set off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal \emph{and} is less effortful.
SVs of ER Strategies could be helpful to describe the ER repertoire\textsuperscript{9} more comprehensively.
Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
This would mean that all strategies are a good option for goal achievement.
A second person with less flexibilty, however, would show high SVs only for one strategy, or for no strategy at all.
This in turn would mean that no strategy is a good choice to achieve goals.

However, so far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
To investigate this question, the individual subjective values of each strategy available for selection would have to be determined.
Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.\\
Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED).\textsuperscript{17}

\hypertarget{er-strategy-discounting}{%
\subsection{1.1 ER strategy discounting}\label{er-strategy-discounting}}

In the original study by Westbrook et al.,\textsuperscript{17} cognitive load was varied using the \emph{n}-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
Participants had to decide whether they wanted to repeat a higher \emph{n}-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward.
In the current study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest \emph{n}-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies.\textsuperscript{14}
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which preceeds the other steps and where the option with the higher subjective value is determined.
In this step, the same monetary value (i.e., 1 EUR) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 EUR) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al.\textsuperscript{17} until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see figure 1).
Additionally, we will test our adapted paradigm in a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al., \ldots).

@@

The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at github.com/ChScheffel/COG-ER-ED.
According to the 21-word-solution, ``we report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study'' in compliance with the 21-word-solution of open science.\textsuperscript{18}
A complete list of all measures assessed in the study will be found at the OSF (\url{https://osf.io/vnj8x/}) and GitHub (github.com/ChScheffel/COG-ER-ED).
All procedures performed in this study were in accordance with the ethical standards of the institutional and/or national research committee and with the 1964 Helsinki declaration and its later amendments or comparable ethical standards.

@@

@@

Young, healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{19} at the Technische Universität Dresden.
Participants will be invited to fill out an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which take place in a shielded cabin with constant lighting.
Before each session, participants receive information about the respective experimental procedure and provide informed consent.
At the beginning of the first session participants fill out a demographic questionnaire and complete an n-Back task with the levels one to four.
Then, they complete an ED procedure on screen, followed by a random repetition of one n-back level.
The second session, containing the ER paradigm, takes place exactly one week after session one.
Participants provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training ensures that all participants are able to implement the ER strategies.
Next, electrodes to measure EMG are being attached and the ER paradigm is conducted.
Participants receive 30.00€ or course credit as compensation.
Study data are being collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden.\textsuperscript{20,21}

@@

The online survey contains a number of questionnaires: General psychological well-being is assessed using the German version of the WHO-5 scale.\textsuperscript{22,23}
To capture the construct of resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{26} is used.
Dispositional use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ).\textsuperscript{6,27}
For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER).\textsuperscript{28}
Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from.\textsuperscript{29}
To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{30,31} is used.
To assess self-control, sum scores of the German versions of the following questionnaires are used:\textsuperscript{32} the Self-Regulation Scale (SRS),\textsuperscript{33} the Brief Self-Control Scale (BSCS);\textsuperscript{34}{]},\textsuperscript{35} and the Barratt Impulsiveness Scale (BIS-11).\textsuperscript{36,37}
Attentional control is assessed using the Attentional Control Scale (ACS).\textsuperscript{38}

@@

Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS)\textsuperscript{39} and the International Affective Picture System (IAPS).\textsuperscript{40}
The 20 neutral pictures (Valence (V): \emph{M} \(\pm\) \emph{SD} = 4.81 \(\pm\) 0.51; Arousal (A): \emph{M} \(\pm\) \emph{SD} = 3 \(\pm\) 0.65) depicted content related to the categories persons, objects, and scenes.
Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used.
An evolutionary algorithm\textsuperscript{41} was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
A complete list of all pictures and their classification into sets can be found in supplementary material X.

\hypertarget{electromyography}{%
\subsubsection{2.3.4 Electromyography}\label{electromyography}}

Two bipolar electromyograph (EMG) measures will be recorded in the region of the \emph{corrugator supercilii} and the \emph{levator labii} using Brain Vision Recorder (Brain Products Inc., Gilching, Germany).
Passive surface Ag/AgCl electrodes (0.7 mm diameter, 10 mm distance between electrodes) filled with electrolyte gel will be used.
Data will be sampled at 1000 Hz.
To measure \emph{corrugator EMG}, electrodes will be applied to the abraded and cleaned skin on the left \emph{corrugator supercilii}, and to measure \emph{levator EMG}, electrodes were applied in the region of the \emph{levator labii}.
The ground electrode will be placed at the left \emph{Mastoid}.
A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter will be applied to both signals.
Afterwards, the signals will be rectified and segmented.
EMG data will be baseline-corrected to -200 ms to 0 ms to stimulus onset.
Last, the sampling rate is changed to 100 Hz and the AUC for the interval of 6000 ms stimulus presentation extracted for every stimulus.

@@

Participants will be healthy adults in the age of 18 to 30, recruited using the software \emph{ORSEE}\textsuperscript{19} at the Technische Universität Dresden.
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Sample size calculation is done using \emph{G*Power}.\textsuperscript{42,43}
In a meta-analysis of Zaehringer and colleagues,\textsuperscript{5} effect sizes of ER on peripheral-physiological measures were reported.
To find an effect of \(d=-0.32\) of ER on \emph{corrugator} muscle activity with \(\alpha=.05\) and \(\beta=.95\), data of least \(N=85\) have to be analyzed.
Power analyses of all other hypotheses yielded smaller sample sizes.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
Therefore, we aim to collect data of 90 participants.

@@

All statistical analyses will be performed using \emph{RStudio} (version 1.4.1717)\textsuperscript{44}and \emph{R} (version 4.1.0)\textsuperscript{45} for Windows.
The level of significance was set to \(\alpha=.05\).

\emph{Effects of emotion regulation on arousal and effort} To examine impact of valence of emotional pictures on subjective arousal, an repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for strategy active viewing will be conducted for behavioral data (subjective arousal ratings).
To investigate the effect of the tree ER strategies on subjective arousal, another rmANOVA was conducted with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings of negative pictures.
To examine the impact of valence on the emotional facial reaction, an rmANOVA with the factor valence (neutral and negative) for strategy active viewing was conducted for EMG activity of \emph{corrugator} and \emph{levator}.
A further rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) was conducted for EMG activity to examine the effects of ER strategies on the emotional facial reaction.
To examine the effect of ER strategies on cognitive effort, an rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings was conducted.
Greenhouse-Geisser-corrected \(p\)-values and degrees of freedom were reported when assumption of sphericity was violated.
Proportion of explained variance \(\eta_{p}^{2}\) was reported as a measure of effect size.
If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.

\emph{Subjective values of emotion regulation strategies} For each ER strategy, SVs were calculated as follows: first, the value 0.015625 was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
Second, the resulting (monetary) value will be divided by 2.00 €.
The final SV for each participant will be computed by averaging all final SVs of each strategy.
The resulting values will be entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression) to explore for group effects.
Again, estimated, marginal means will be computed as post-hoc contrasts.

>>>>

Every day we are confronted with stressful or emotionally demanding situations.
The ability to modify emotional experiences, expressions, and physiological reactions\textsuperscript{1} to regulate emotions is an important cognitive skill.
It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning.\textsuperscript{2}
Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification,\textsuperscript{1} and, following the taxonomy of Powers and LaBar,\textsuperscript{3} individuals can implement ER strategies by means of different tactics.
So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process.\textsuperscript{1}
In contrast, response modification takes place late in the process and is therefore conceptualized as a response-focused strategy.\textsuperscript{1}
This postulated temporal sequence of ER strategies influences their effectiveness.
It is meta-analytically proven that all mentioned strategies reduce subjective emotional arousal.\textsuperscript{4}
Distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed small to medium effect sizes on measures of emotional experience (distraction: \emph{d\textsubscript{+}} = 0.27; suppression: \emph{d\textsubscript{+}} = 0.27).
Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of \emph{d\textsubscript{+}} = 0.45.\textsuperscript{4}
Moreover it is known that ER strategies reduce physiological arousal, measured via electromyography (EMG) in the region of the \emph{corrugator supercilii}.\textsuperscript{5}
So these tactics from three different strategies proved to be effective in the short term.
However, in order to be able to make a statement on their general benefit, longer-term consequences must also be considered.
Especially strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
Long-term consequences of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed.\textsuperscript{6}
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of \emph{adaptive} and \emph{maladaptive} strategies.
For example, it could be shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms.\textsuperscript{7}
Also, a number of ER strategies is linked to psychological disorders (for meta-analytic review, see Aldao et al.).\textsuperscript{8}

The postulation of \emph{adaptive} and \emph{maladaptive} strategies was put in a new perspective with the concept of ER flexibility.
Similar to other psychological domains, e.g., attention and goal pursuit, \emph{maladaptive} now refers to inflexible strategy use or use of strategies that are hindering the achievement of goals.\textsuperscript{9}
Adaptive flexible ER requires having a large repertoire of ER strategies.\textsuperscript{9}
For example, greater ER variability is related to reduced negative affect and therefore beneficial in daily life.\textsuperscript{10}
Strategies have to be chosen from the repertoire that are useful for goal achieving.
Evidence from other contexts (e.g., intertemporal choice,)\textsuperscript{11} shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs.
For example, it was shown that the intensity of a stimulus or situation plays a role in the choice.\textsuperscript{12}
Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction.\textsuperscript{12,13}
Further influencing factors are for example extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort.\textsuperscript{13,14}
Especially for effort, in our previous work we could show that the choice for an ER strategy is mainly influenced by the effort required to implement a given strategy.\textsuperscript{14}
In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards they could choose, which strategy they want to use again.
Participants tended to re-apply the strategy that was subjectively less effortful, even though it was subjectively not the most effective one - in this case: suppression.
Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
What has been missing in research on ER choice so far is information regarding the strategy \emph{not} chosen.
People choose a strategy that they prefer for different, relatively well-known reasons.
However, nothing is revealed about the strategy that is \emph{not chosen}.

The postulation of \emph{adaptive} and \emph{maladaptive} strategies was put into a new perspective with the concept of ER flexibility.
Similar to other psychological domains such as attention and goal pursuit, \emph{maladaptive} now refers to inflexible strategy use or the use of strategies that are hindering the achievement of goals.\textsuperscript{9}
In contrast, \emph{adaptive} ER requires having a large repertoire of ER strategies to choose from\textsuperscript{9} and choosing the strategy that is useful for goal achievement in a particular situation.
This greater ER variability has been shown to be related to reduced negative affect.\textsuperscript{10}
The process of choosing an ER strategy from one's own repertoire likely shares similarities with other contexts such as intertemporal choice, in which individuals assign subjective values to every choice option.\textsuperscript{11}
Additionally, there are ER-specific influences on choice behaviour such as the intensity of the stimulus or situation, which leads to a choice of rather disengaging strategies like distraction, extrinsic motivation (e.g., monetary incentives), motivational determinants (i.e., hedonic regulatory goals), and effort.\textsuperscript{13,14}
Effort in particular appeared to be the main factor in ER choice behaviour in our previous work.\textsuperscript{14}
In that study, participants used the strategies distancing and suppression while inspecting emotional pictures, and could choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one for them - in this case: Suppression.
Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
Research on ER choice has shown that individuals choose a strategy that they prefer for different, relatively well-known reasons.
However, nothing has been investigated regarding the strategy that is \emph{not} chosen.

We assume that people choose the strategy that has the highest value for them at that moment.
The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement.\textsuperscript{9}
One certainly central goal is the regulation of negative affect.
A second, intrinsic and rather less obvious goal is the avoidance of effort.\textsuperscript{15}
When given the choice, most individuals prefer tasks that are less effortful.\textsuperscript{16}
We assume that both aspects are traded off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal \emph{and} is less effortful.
SVs of ER Strategies could be helpful to describe the ER repertoire\textsuperscript{9} more comprehensively.
Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
This would mean that all strategies are a good option for goal achievement.
A second person with less flexibilty, however, would show high SVs only for one strategy, or for no strategy at all.
This in turn would mean that no strategy is a good choice to achieve ER goals.

However, so far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
To investigate this question, the individual SVs of each strategy available for selection would have to be determined.
Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.\\
Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED).\textsuperscript{17}

In the original study by Westbrook et al.,\textsuperscript{17} cognitive load was varied using the \emph{n}-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli.
Participants had to decide in an iterative procedure whether they wanted to repeat a higher \emph{n}-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption taht teh objectively easiest \emph{n}-back level has the highest SV.
In the current study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest \emph{n}-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies.\textsuperscript{14}
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which preceeds the other steps and where the option with the higher subjective value is determined.
In this step, the same monetary value (i.e., 1 €) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al.\textsuperscript{17} until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see figure 1).
Additionally, we will test our adapted paradigm in a \emph{n}-back task and explore whether this paradigm can describe individuals that do not prefer the easiest \emph{n}-back option (see Zerna et al., \ldots).

@@

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.\textsuperscript{18}
The paradigm was written and presented using \emph{Psychopy}.\textsuperscript{19}
We used \emph{R} with \emph{R Studio}\textsuperscript{20,21} with the main packages \ldots{} for all our analyses.
The R Markdown file used to analyze the data and write this document, as well as the raw data and the materials are freely available at \url{https://github.com/ChScheffel/CERED}.
A complete list of all measures assessed in the study can be found at OSF (\url{https://osf.io/vnj8x/}) and GitHub (\url{https://github.com/ChScheffel/CERED}).

@@

The study protocol complies with all relevant ethical regulations and was approved by the ethics committee of the Technische Universität Dresden (reference number EK\ldots).
Prior to testing, written informed consent will be obtained.
Participants will receive 30€ in total or course credit for participation.

@@

Young, healthy participants (aged 18 to 30 years) will be recruited using the software \emph{ORSEE}\textsuperscript{22} at the Technische Universität Dresden.
Participants will be invited to compete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which take place in a shielded cabin with constant lighting.
Before each session, participants receive information about the respective experimental procedure and provide informed consent.
At the beginning of the first session participants fill out a demographic questionnaire and complete an n-Back task with the levels one to four.
Then, they complete an effort discounting (ED) procedure on screen, followed by a random repetition of one n-back level.
The second session, containing the ER paradigm, takes place exactly one week after session one.
Participants provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training ensures that all participants are able to implement the ER strategies.
Next, electrodes to measure EMG being attached and the ER paradigm is conducted.
Participants receive 30.00€ or course credit as compensation.
Study data are being collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden.\textsuperscript{23,24}

@@

The online survey contains a number of questionnaires: General psychological well-being is assessed using the German version of the WHO-5 scale.\textsuperscript{25,26}
To capture the construct of resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)\textsuperscript{29} is used.
Dispositional use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ).\textsuperscript{6,30}
For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER).\textsuperscript{31}
Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from.\textsuperscript{32}
To assess Need for Cognition, the German version short form of the Need for Cognition Scale\textsuperscript{33,34} is used.
To assess self-control, sum scores of the German versions of the following questionnaires are used:\textsuperscript{35} the Self-Regulation Scale (SRS),\textsuperscript{36} the Brief Self-Control Scale (BSCS);\textsuperscript{37}{]},\textsuperscript{38} and the Barratt Impulsiveness Scale (BIS-11).\textsuperscript{39,40}
Attentional control is assessed using the Attentional Control Scale (ACS).\textsuperscript{41}

@@

Pictures used in the paradigm were selected from the Emotional Picture Set (EmoPicS)\textsuperscript{42} and the International Affective Picture System (IAPS).\textsuperscript{43}
The 20 neutral pictures (Valence (V): \emph{M} \(\pm\) \emph{SD} = 4.81 \(\pm\) 0.51; Arousal (A): \emph{M} \(\pm\) \emph{SD} = 3 \(\pm\) 0.65) depicted content related to the categories persons, objects, and scenes.
Further, 100 negative pictures, featuring categories animals, body, disaster, disgust, injury, suffering, violence, and weapons, were used.
An evolutionary algorithm\textsuperscript{44} was used to cluster these pictures into five sets with comparable valence and arousal values (set one: V: \emph{M} \(\pm\) \emph{SD} = 2.84 \(\pm\) 0.57, A: \emph{M} \(\pm\) \emph{SD} = 5.62 \(\pm\) 0.34; set two: V: \emph{M} \(\pm\) \emph{SD} = 2.64 \(\pm\) 0.46, A: \emph{M} \(\pm\) \emph{SD} = 5.58 \(\pm\) 0.35; set three: V: \emph{M} \(\pm\) \emph{SD} = 2.82 \(\pm\) 0.62, A: \emph{M} \(\pm\) \emph{SD} = 5.60 \(\pm\) 0.39; set four: V: \emph{M} \(\pm\) \emph{SD} = 2.65 \(\pm\) 0.75, A: \emph{M} \(\pm\) \emph{SD} = 5.61 \(\pm\) 0.41; set five: V: \emph{M} \(\pm\) \emph{SD} = 2.74 \(\pm\) 0.70, A: \emph{M} \(\pm\) \emph{SD} = 5.63 \(\pm\) 0.37).
A complete list of all pictures and their classification into sets can be found in supplementary material X.

\hypertarget{facial-electromyography}{%
\subsubsection{2.3.4 Facial electromyography}\label{facial-electromyography}}

Bipolar facial electromyography (EMG) will be measured for \emph{corrugator supercilii} and \emph{levator labii} as indices of affective valence (Bradley \& Lang, 2000).
Two passive surface Ag/AgCl electrodes (8 mm inner diameter, 10 mm distance between electrodes) will be placed over each left muscle according to the guidelines of Fridlund and Cacioppo (1986).
The ground electrode will be placed over the left \emph{Mastoid}.
Before electrode placement, the skin will be abraded with Every abrasive paste, cleaned with alcohol, and filled with Lectron III electrolyte gel.
Raw signals will be amplified by a BrainAmp amplifier (Brain Products Inc., Gilching, Germany).
Impedance level will be kept below 10 \(k\Omega\).
Data will be sampled at 1000 Hz, filtered, rectified and integrated.
A 20 Hz high pass (order 8), a 300 Hz low pass (order 8), and a 50 Hz notch filter will be applied to both signals.
Corrugator and Levator EMG will be analyzed during the 6 s of picture presentation.
EMG data will be baseline-corrected using a time window of 2 s prior to stimulus onset (cf.~Bradley \& Lang, 2000).
Last, the sampling rate will be changed to 100 Hz, and EMG data will be averaged for each condition and each participant.

@@

Participants will be healthy adults in the age of 18 to 30, recruited using the software \emph{ORSEE}\textsuperscript{22} at the Technische Universität Dresden.
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Sample size calculation is done using \emph{G*Power}.\textsuperscript{45,46}
In a meta-analysis of Zaehringer and colleagues,\textsuperscript{5} effect sizes of ER on peripheral-physiological measures were reported.
To find an effect of \(d=-0.32\) of ER on \emph{corrugator} muscle activity with \(\alpha=.05\) and \(\beta=.95\), data of least \(N=85\) have to be analyzed.
Power analyses of all other hypotheses yielded smaller sample sizes.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
Therefore, we aim to collect data of 90 participants.

@@

All statistical analyses will be performed using \emph{RStudio} (version 1.4.1717)\textsuperscript{21}and \emph{R} (version 4.1.0)\textsuperscript{20} for Windows.
The level of significance will be set to \(\alpha=.05\).

\emph{Effects of emotion regulation on arousal, facial EMG and effort} To examine the impact of valence of emotional pictures on subjective arousal ratings, a repeated measures analysis of variance (rmANOVA) with the factor valence (neutral and negative) for the strategy active viewing will be conducted.
To investigate the effects of the three ER strategies on subjective arousal, another rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective arousal ratings will be conducted.

To examine the impact of valence on facial EMG, a rmANOVA with the factor valence (neutral and negative) for the strategy active viewing will be conducted for \emph{corrugator} and \emph{levator} activity.
To examine the effects of the three ER strategies on facial EMG, another rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for \emph{corrugator} and \emph{levator} activity will be conducted.

To examine the effect of ER strategies on cognitive effort, a rmANOVA with the factor strategy (active viewing, distraction, distancing, and suppression) for subjective effort ratings will be conducted.
Greenhouse-Geisser-corrected \(p\)-values and degrees of freedom will be reported when the assumption of sphericity is violated.
Proportion of explained variance \(\eta_{p}^{2}\) will be reported as a measure of effect size.
If indicated by the data, estimated marginal means will be computed as post-hoc contrasts.

\emph{Subjective values of emotion regulation strategies} For each ER strategy, SVs will be calculated as follows: first, the value 0.015625 will be added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
Second, the resulting (monetary) value will be divided by 2.00 €.
The final SV for each participant will be computed by averaging all final SVs of each strategy.
The resulting values will be entered in a rmANOVA to compare the SVs of the three strategies (distraction, distancing, and suppression) to explore for group effects.
Again, estimated, marginal means will be computed as post-hoc contrasts.
